### 2020-06-02 5_evaluation.tex
Tighten text.

One advantage of asynchronous execution is
the ability to mitigate load imbalance with little or no additional programmer effort, especially in the presence of
task parallelism. To quantify this effect,
Figure~\ref{fig:efficiency-imbalance} plots task granularity vs
efficiency curves under load imbalance where each task's duration is multiplied by a uniform random variable between [0,~1). The task durations are generated with a deterministic
pseudo random number generator with a consistent seed to ensure
identical task durations for all systems.

The MPI implementation of Task Bench, with its distinct computation and communication phases,
suffers the most under load imbalance. The biggest
difference is at large task granularities, where the imbalance
effectively puts an upper bound on MPI efficiency. At smaller task
granularities the effect shrinks and may even reverse as systems hit
their fundamental limits due to overhead.

@@

>>>>

One advantage of asynchronous execution is
the ability to mitigate load imbalance with little or no additional programmer effort, especially in the presence of
task parallelism. To quantify this effect,
Figure~\ref{fig:efficiency-imbalance} plots task granularity vs
efficiency under load imbalance where each task's duration is multiplied by a uniform random variable in [0,~1). Task durations are generated with a deterministic
pseudo random number generator with a consistent seed to ensure
identical durations for all systems.

The MPI Task Bench, with its distinct computation and communication phases,
suffers the most under load imbalance. The biggest
difference is at large task granularities, where the imbalance
effectively puts an upper bound on efficiency. At smaller task
granularities the effect shrinks and may even reverse as systems hit
their fundamental limits due to overhead.

@@

\input{e9_strong}

{\color{blue}
\subsection{Predicting Strong Scaling with METG}

% Summary:

% Charm++:
% Limit/Ideal intersects at: 55 nodes, 0.068 s
% Limit/Actual intersects at: 67 nodes, 0.086 s
% Limit/Ideal vs Limit/Actual gap in nodes: 1.22x
% Limit/Ideal vs Limit/Actual gap in time: 1.27x

% Overall (out of 11 systems that perform well enough to have an intersection):
% Limit/Ideal vs Limit/Actual gap in nodes:
%   mean: 1.61x
%   median: 1.60x
%   min: 1.13x
%   max: 2.19x
% Limit/Ideal vs Limit/Actual gap in time:
%   mean: 1.28x
%   median: 1.27x
%   min: 1.01x
%   max: 1.69x

We can use METG to predict the scalability of a code. Figure
\ref{fig:strong-scaling} shows strong scaling for three Task Bench
implementations with the stencil pattern. Lines marked ``actual''
represent strong scaling measurements, while ones marked ``limit'' are
computed by multiplying METG(50\%) by tasks per core (in this case,
1000). Intuitively, ``limit'' is the smallest time to solution that
can be achieved for \emph{any} problem size at that node count, while
maintaining 50\% efficiency. Note that ``actual'' eventually falls
below ``limit'' because ``actual'' is not constrained to 50\%
efficiency and eventually drops below this level.

There are two points of interest on each ``limit'' curve: the point
where it intersects ``actual'' and the point where it intersects an
ideal scaling curve, computed by taking the initial time to solution
and assuming linear scaling. These points are marked in
Figure~\ref{fig:strong-scaling} with a black square and black circle,
respectively. Notably, the intersection between ideal and ``limit''
requires only a single node run, along with measurements of METG(50\%)
at each node count. Using this data it is possible to predict the
strong scalability of the code: i.e., the smallest time to solution,
and the number of nodes at which that time is achieved, while
maintaining at least 50\% efficiency. In
Figure~\ref{fig:strong-scaling} this can be seen as the distance
between the black square and circle; these are separated by a factor of
$1.22\times$ in node count, and $1.27\times$ in time to solution.

When we consider all 11 programming systems that scale well enough to
perform this experiment, we find that the average separation between
the ideal and actual intersection points is $1.61\times$ in node count
(max $2.19\times$, min $1.13\times$) and $1.28\times$ in time to
solution (max $1.69\times$, min $1.01\times$).

} % color
